---
title: "Reproducible Documents"
author: "Ingrid M Wagnon"
format: html
---

## About me

-   Ingrid M. Wagnon
-   Roskilde University

I have a **PhD in Neurosciences**. I currently work as a post-doc on a project about *food-derived miRNA*.


## Simple Code

```{r Simple Multiplication}
3 * 3
```


## About Git

Click on the Git app -\> Commit -\> Stage the file that you want to commit and then the first commit entry could be "Initial Commit" -\> Click "Commit"

### Testing Git

Try to commit


## Setup Code Chunk

When you insert a code chunk "{r}" appears. You can add a name next to it (with a space) and it will label/name your code chunk.

```{r setup}
library(tidyverse)
post_meal_data <- read_csv2(here::here("data/post-meal-insulin.csv"))
```

The "here::here" function defines the path of access to the data set as inside the project folder so it is not a "personal" path - Makesit more homogeneous to reuse the project file rather than have the path directory towards somewhere else in your computer.

For the "read_csv2" it is because the data are separated by semicolons instead of coma.


## Showing the Data

You can use Tab for autocompletion (giving you the name of items already define so you don't need to type them entirely)

```{r}
post_meal_data
glimpse(post_meal_data)
```




